### 2022-05-11 main/chapter_2ljets.tex
begin adding sections and quotes

\chapterquote{Laws were made to be broken.}%
{Christopher North, 1785--1854}%: Blackwood's Magazine May 1830

>>>>

\chapterquote{An experiment is never a failure solely because it fails to
achieve predicted results. An experiment is a failure only when it also
fails adequately to test the hypothesis in question, when the data it
produces don’t prove anything one way or another}%
{Robert M. Pirsig~\cite{pirsig1999zen}}

### 2022-05-11 main/chapter_experiment.tex
set out chapters, add front quote
begin adding sections and quotes

\chapter{A search for new phenomena}
\label{chapter:2ljets}

\chapterquote{Laws were made to be broken.}%
{Christopher North, 1785--1854}%: Blackwood's Magazine May 1830

@@

\clearpage

Hello again

>>>>

\chapter{The ATLAS experiment}
\label{chapter:experiment}

\chapterquote{%
if observing outer space gives us a view of the past, observing inner space
would surely give us a glimpse into the future - would be interesting if NASA
made a telescope for that%
}%
{Ken M}

@@

### 2022-05-11 main/chapter_searches.tex
set out chapters, add front quote
begin adding sections and quotes

\chapter{The ATLAS experiment}
\label{chapter:experiment}

\chapterquote{Laws were made to be broken.}%
{Christopher North, 1785--1854}%: Blackwood's Magazine May 1830

Hello

>>>>

\chapter{Searches in ATLAS}
\label{chapter:intro}

\chapterquote{%
Within this theory, statistical methods of great practical usefulness have been
developed, and its statements can and frequently do contribute in a vague way
to the interpretation of data. \ldots%
}%
{John W. Pratt~\cite{pratt1961testing}}

\section{Data analysis}

\subsection{Frequentist methods}

\chapterquote{%
\ldots But this book, by its very excellence, its thoroughness, lucidity and
precision, intensifies my growing feeling that nevertheless the theory is
arbitrary, be it however ``objective,'' and the problems it solves, however
precisely it may solve them, are not even simplified theoretical counterparts
of the real problems to which it is applied.%
}%
{John W. Pratt~\cite{pratt1961testing}}

\subsection{Post-frequentist methods}

\section{Searches}

### 2022-05-11 main/chapter_theory.tex
set out chapters, add front quote
begin adding sections and quotes

\chapter{Practice of searches in ATLAS}
\label{chapter:intro}

\chapterquote{Laws were made to be broken.}%
{Christopher North, 1785--1854}%: Blackwood's Magazine May 1830

@@

\clearpage

Hello again

>>>>

\chapter{The Standard Model and beyond}
\label{chapter:theory}

\chapterquote{%
The idea that theorems follow from the postulates does not correspond to simple
observation.
If the Pythagorean theorem were found to not follow from the postulates, we
would again search for a way to alter the postulates until it was true.
Euclid's postulates came from the Pythagorean theorem, not the other way.}%
{Richard Hamming~\cite{hamming1980unreasonable}}

\chapterquote{%
One geometry can not be more true than another; it can only be more convenient.
Geometry is not true, it is advantageous.}%
{Robert M. Pirsig~\cite{pirsig1999zen}}

% Standard Model past present future

@@

\section{Particles}

\section{The Standard Model}

\section{Supersymmetric models}

\subsection{Minimal supersymmetric models}

\subsection{Guage Mediated Supersymmetry Breaking}

### 2022-05-11 main/frontmatter.tex
set out chapters, add front quote
begin adding sections and quotes

\titlepage[of Homerton College]{%
  A dissertation submitted to the University of Cambridge\\ for the degree of Doctor of Philosophy}

@@

\begin{declaration}
This dissertation is the result of my own work, except where explicit
reference is made to the work of others, and has not been submitted
for another qualification to this or any other university. This
dissertation does not exceed the word limit for the respective Degree
Committee.
\vspace*{1cm}
\begin{flushright}
Your Name
\end{flushright}
\end{declaration}

\begin{acknowledgements}
Of the many people who deserve thanks, some are particularly prominent,
such as my supervisor\dots
This thesis was made in \LaTeXe{} using the ``hepthesis'' class~\cite{hepthesis}.
\end{acknowledgements}

@@

\thispagestyle{empty}

>>>>

\titlepage[of Homerton College]{%
A dissertation submitted to the University of Cambridge\\
for the degree of Doctor of Philosophy%
}

@@

\begin{declaration}
This dissertation is the result of my own work, except where explicit
reference is made to the work of others, and has not been submitted
for another qualification to this or any other university. This
dissertation does not exceed the word limit for the respective Degree
Committee.
\vspace*{1cm}
\begin{flushright}
Rupert Tombs
\end{flushright}
\end{declaration}

\begin{acknowledgements}
Of the many people who deserve thanks, some are particularly prominent,
such as my supervisor\dots
\\
This document uses parts of the ``hepthesis'' class~\cite{hepthesis}.
\end{acknowledgements}

@@

\pagequote{%
Begin reading at Chapter N.
Do \textbf{not} read the quotations that appear at the\\
beginning of the chapter.%
}%
{Donald E. Knuth~\cite{knuth1975art}}

% the following blank page should also have no page number
\thispagestyle{empty}
